|

### 2022-12-20 paper.Rmd
Mon Dec 19 21:00:08 CET 2022: update-remote.sh
Tue Dec 20 09:00:07 CET 2022: update-remote.sh

>>>>

![Airfoil - First Generation Median Training Error for variable number of hidden Layers](./img/airfoil_firstGen/airfoil_firstGen_mean_training_error_by_layers.png)

![Airfoil - First Generation final Training Error for variable number of hidden Layers](./img/airfoil_firstGen/airfoil_firstGen_boxplot_training_error_by_layer.png)

### 2022-12-20 paper.tex
Tue Dec 20 09:00:07 CET 2022: update-remote.sh

\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

@@

Johannes Gutenberg University Mainz}
\author{}
\date{\vspace{-2.5em}Date of Submission: 2022-12-18}

@@

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\setcounter{page}{1}
\tableofcontents
\thispagestyle{empty}
\newpage  
\listoftables
\listoffigures
\thispagestyle{empty}
\newpage

@@

\caption{(\#tab:airfoil_dataset_description)Airfoil - Dataset Description}
\centering
\begin{tabular}[t]{l|l|l|l}
\hline
\textbf{Type} & \textbf{Name} & \textbf{Description} & \textbf{Unit}\\
\hline
input & x1 & Frequency & Hertz\\
\hline
input & x2 & Angle of attack & Degree\\
\hline
input & x3 & Chord length & meters\\
\hline
input & x4 & Free-stream velocity & meters/second\\
\hline
input & x5 & Suction side displacement thickness & meters\\
\hline
output & y & Scaled sound pressure level & decibels\\
\hline
\end{tabular}
\end{table}

@@

\caption{(\#tab:airfoil_function_set)Airfoil - Function Set}
\centering
\begin{tabular}[t]{l|r}
\hline
\textbf{function.} & \textbf{arity}\\
\hline
addition & 2\\
\hline
subtraction & 2\\
\hline
multiplication & 2\\
\hline
analytic\_quotient & 2\\
\hline
\end{tabular}
\end{table}

@@

>>>>

@@

Johannes Gutenberg University Mainz}
\author{}
\date{\vspace{-2.5em}Date of Submission: 2022-12-19}

@@

\setcounter{page}{1}
\tableofcontents
\thispagestyle{empty}
\newpage  
\listoftables
\listoffigures
\thispagestyle{empty}
\newpage

@@

\caption{\label{tab:airfoil_dataset_description}Airfoil - Dataset Description}
\centering
\begin{tabular}[t]{l|l|l|l}
\hline
\textbf{Type} & \textbf{Name} & \textbf{Description} & \textbf{Unit}\\
\hline
input & x1 & Frequency & Hertz\\
\hline
input & x2 & Angle of attack & Degree\\
\hline
input & x3 & Chord length & meters\\
\hline
input & x4 & Free-stream velocity & meters/second\\
\hline
input & x5 & Suction side displacement thickness & meters\\
\hline
output & y & Scaled sound pressure level & decibels\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:airfoil_function_set}Airfoil - Function Set}
\centering
\begin{tabular}[t]{l|r}
\hline
\textbf{function.} & \textbf{arity}\\
\hline
addition & 2\\
\hline
subtraction & 2\\
\hline
multiplication & 2\\
\hline
analytic\_quotient & 2\\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{./img/airfoil_firstGen/airfoil_firstGen_mean_training_error_by_layers.png}
\caption{Airfoil - First Generation Median Training Error for variable
number of hidden Layers}
\end{figure}

\begin{figure}
\centering
\includegraphics{./img/airfoil_firstGen/airfoil_firstGen_boxplot_training_error_by_layer.png}
\caption{Airfoil - First Generation final Training Error for variable
number of hidden Layers}
\end{figure}
